---
title: "Getting Started with turf"
vignette: >
  %\VignetteIndexEntry{Getting Started with turf}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

## What is TURF?

TURF (Total Unduplicated Reach and Frequency) answers the question: *which combination of M items reaches the most people?* Given an N×J binary matrix where `mat[r, c] = 1` means respondent `r` is reached by item `c`, TURF exhaustively evaluates all C(J, M) possible bundles of M items and returns the top-K ranked by reach.

Common applications include product line optimization, content menu design, and feature prioritization — anywhere you want to maximize the share of people who find at least one thing they like.

## Basic Usage

```{r}
library(turf)
data(reach)

# reach is a 3602×12 binary matrix (respondents × items)
dim(reach)
```

Run TURF for bundle sizes 3 through 5, keeping the top 10 results for each size:

```{r}
results <- turf(mat = reach, range = 3:5, keep = 10)
head(results)
```

The output is a `data.table` with one row per result:

| Column | Description |
|--------|-------------|
| `size` | Bundle size (M) |
| `rank` | Rank within that bundle size (1 = highest reach) |
| `reach` | Proportion of respondents reached (0–1) |
| `freq` | Average number of items reaching each respondent |
| `item1` … `itemM` | Column indices of the items in the bundle |

## Multiple Audiences

A common workflow is to run TURF for an overall sample and then for subgroups, with subgroup membership stored as binary columns in a demographics data frame:

```{r}
#| eval: false
res <- list()
res[["overall"]] <- turf(mat)

for (i in names(demos)) {
    res[[i]] <- turf(mat[demos[[i]] == 1, ])
}

output <- dplyr::bind_rows(res, .id = "audience")
```

## Four Execution Modes

`turf()` provides two implementations and two threading modes:

- **Implementation**: C++ (`cpp = TRUE`, default) or pure R (`cpp = FALSE`)
- **Threading**: multi-core (`n_cores > 1`, default) or single-core (`n_cores = 1`)

Multi-core parallelizes across bundle sizes, so the benefit scales with the number of values in `range`. C++ is substantially faster for large problems.

### Small task (range = 3:5)

```{r}
#| eval: false
microbenchmark::microbenchmark(
    `R, 1 core`       = turf(reach, 3:5, n_cores = 1, cpp = FALSE),
    `R, multi-core`   = turf(reach, 3:5, n_cores = 3, cpp = FALSE),
    `C++, 1 core`     = turf(reach, 3:5, n_cores = 1, cpp = TRUE),
    `C++, multi-core` = turf(reach, 3:5, n_cores = 3, cpp = TRUE),
    times = 10
)
```

### Large task (range = 6:8)

```{r}
#| eval: false
microbenchmark::microbenchmark(
    `R, 1 core`       = turf(reach, 6:8, n_cores = 1, cpp = FALSE),
    `R, multi-core`   = turf(reach, 6:8, n_cores = 3, cpp = FALSE),
    `C++, 1 core`     = turf(reach, 6:8, n_cores = 1, cpp = TRUE),
    `C++, multi-core` = turf(reach, 6:8, n_cores = 3, cpp = TRUE),
    times = 10
)
```

**Rule of thumb:** Use the defaults (`cpp = TRUE`, `n_cores = detectCores() - 1`) for most analyses. The pure R fallback is available if you cannot compile C++ on a given machine.
